Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-14 paper/manuscript.Rmd
update P2
generate paper

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond2016],
to avoid predators [@Bergerud1985], and to access islands during calving
[@Bergerud1990]. Even for adept swimmers like caribou, that have hollow hair
shafts that aid in flotation, the energetic expenditure of swimming for
quadrupedal mammals is significantly higher than walking or running, and
drowning is also possible [@Miller1985]. Despite the abundance of coastal and
island caribou herds, only a handful of studies have documented caribou swimming
in the ocean, and most of these lack observation, but rather deduce swimming
based on presence of caribou on a previously uninhabitated island  [e.g.
@Miller1995; @Miller2002; @Jeffery2007; @Ricca2012]. Caribou may swim between
islands in the ocean for similar reasons they swim in freshwater [@Leblond2016],
mainly concerning predator avoidance or to access new habitats. We propose
that one such explanation, the forage limitation hypothesis, is the most likely
explanation for oceanic swimming for caribou that live on islands in the Fogo
Island archipelago.

>>>>

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond2016],
to avoid predators [@Bergerud1985], and to access islands during calving
[@Bergerud1990]. Even for adept swimmers like caribou, that have hollow hair
shafts that aid in flotation, the energetic expenditure of swimming for
quadrupedal mammals is significantly higher than walking or running, and
drowning is also possible [@Miller1985]. Despite the abundance of coastal and
island caribou herds, only a handful of studies have documented caribou swimming
in the ocean, and most of these lack observation, but rather deduce swimming
based on presence of caribou on a previously uninhabitated island  [e.g.
@Miller1995; @Miller2002; @Jeffery2007; @Ricca2012]. Caribou may swim between
islands in the ocean for similar reasons they swim in freshwater [@Leblond2016],
mainly concerning predator avoidance or to access new habitat. We propose
that one such explanation, the forage limitation hypothesis, is the most likely
explanation for oceanic swimming for caribou that live on islands in the Fogo
Island archipelago.
